\author[odu]{S.~Adhikari}
\author[gsi]{A.~Ali}
\author[odu]{M.~Amaryan}
\author[uofa]{E.G.~Anassontzis}
\author[cmu]{A.~Austregesilo}
\author[jlab]{F.~Barbosa}
\author[fsu]{J.~Barlow}
\author[uconn]{A.~Barnes}
\author[fsu]{E.~Barriga}
\author[iu]{R.~Barsotti}
\author[uofr]{T.D.~Beattie}
\author[iu]{D.W.~Bennett}
\author[cua,mephi]{V.V.~Berdnikov}
\author[uncw]{T.~Black}
\author[fiu]{W.~Boeglin}
\author[gwu]{W.J.~Briscoe}
\author[jlab]{T.~Britton}
\author[jlab]{J.~Brock}
\author[usm]{W.K.~Brooks}
\author[fsu]{B.E.~Cannon}
\author[jlab]{C.~Carlin}
\author[jlab]{D.S.~Carman}
\author[ihep]{N.~Cao}
\author[itep]{O.~Chernyshov}
\author[jlab]{E.~Chudakov}
\author[asu]{S.~Cole}
\author[gwu]{O.~Cortes}
\author[fsu]{V.~Crede}
\author[jlab]{M.M.~Dalton}
\author[uncw]{T.~Daniels}
\author[jlab]{A.~Deur}
\author[jlab]{C.~Dickover}
\author[fsu]{S.~Dobbs}
\author[itep]{A.~Dolgolenko}
\author[fiu]{R.~Dotel}
\author[asu]{M.~Dugger}
\author[gsi]{R.~Dzhygadlo}
\author[iu]{A.~Dzierba\fnref{f0}}
\fntext[f0]{Current address: Dzierba.}
\author[jlab]{H.~Egiyan}
\author[fiu]{T.~Erbora}
\author[fsu]{A.~Ernst}
\author[fsu]{P.~Eugenio}
\author[mit]{C.~Fanelli}
\author[gwu]{S.~Fegan\fnref{f1}}
\fntext[f1]{Current address: University of York, York YO10 5DD, United Kingdom.}
\author[uofr]{A.M.~Foda}
\author[iu]{J.~Foote}
\author[iu]{J.~Frye}
\author[jlab]{S.~Furletov}
\author[uncw]{L.~Gan}
\author[ncatsu]{A.~Gasparian}
\author[itep]{A.~Gerasimov}
\author[yerevan]{N.~Gevorgyan}
\author[iu]{C.~Gleason}
\author[gsi]{K.~Goetzen}
\author[fsu]{A.~Goncalves}
\author[itep]{V.S.~Goryachev}
\author[fiu]{L.~Guo}
\author[usm]{H.~Hakobyan}
\author[gsi]{A.~Hamdi}
\author[mit]{J.~Hardin}
\author[fsu]{A.~Henderson}
\author[uofr]{C.L.~Henschel\fnref{f2}}
\fntext[f2]{Current address:Henschel.}
\author[uofr]{G.M.~Huber}
\author[wm]{A.~Hurley}
\author[glasgow]{D.G.~Ireland}
\author[jlab]{M.M.~Ito}
\author[cmu]{N.S.~Jarvis}
\author[uconn]{R.T.~Jones}
\author[yerevan]{V.~Kakoyan}
\author[uofr]{S. ~Katsaganis\fnref{f3}}
\fntext[f3]{Current address: Katsaganis.}
\author[cua]{G.~Kalicy}
\author[fiu]{M.~Kamel}
\author[jlab]{C.D.~Keith}
\author[cua]{F.J.~Klein\fnref{f4}}
\fntext[f4]{Current address: Office of Academic Computing Services, University of Maryland, College Park, MD 20742.}
\author[gsi]{R.~Kliemt}
\author[uofr]{D.~Kolybaba}
\author[uofa]{C.~Kourkoumelis}
\author[uofr]{S.T.~Krueger\fnref{f5}}
\fntext[f5]{Current address: Krueger.}
\author[usm]{S.~Kuleshov}
\author[iu]{M.~Lara\fnref{f6}}
\fntext[f6]{Current address: Lara.}
\author[umass,itep]{I.~Larin}
\author[jlab]{D.~Lawrence}
\author[iu]{J.P.~Leckey\fnref{f7}}
\fntext[f7]{Current address: NASA.}
\author[fsu]{D.I.~Lersch}
\author[uofr]{B.D.~Leverington\fnref{f8}}
\fntext[f8]{Current address: Leverington.}
\author[cmu]{W.I.~Levine}
\author[wm]{W.~Li}
\author[ihep]{B.~Liu}
\author[glasgow]{K.~Livingston}
\author[uofr]{G.J.~Lolos}
\author[tomsk,tomskb]{V.~Lyubovitskij}
\author[jlab]{D.~Mack}
\author[yerevan]{H.~Marukyan}
\author[jlab]{P.T.~Mattione\fnref{f9}}
\fntext[f9]{Current address: Deep Silver Volition, 1 E Main St., Champaign, IL 61820.}
\author[itep]{V.~Matveev}
\author[jlab]{M.~McCaughan}
\author[cmu]{M.~McCracken}
\author[cmu]{W.~McGinley}
\author[uconn]{J.~McIntyre}
\author[jlab]{D.~Meekins}
\author[usm]{R.~Mendez}
\author[cmu]{C.A.~Meyer}
\author[umass]{R.~Miskimen}
\author[iu]{R.E.~Mitchell}
\author[uconn]{F.~Mokaya}
\author[asu]{K.~Moriya}
\author[gsi]{F.~Nerling}
\author[fsu]{L.~Ng}
\author[gwu]{H.~Ni}
\author[uofr]{N.~Ochoa}
\author[fsu]{A.I.~Ostrovidov}
\author[uofr]{Z.~Papandreou}
\author[mit]{M.~Patsyuk}
\author[fiu]{C.~Paudel}
\author[glasgow]{P.~Pauli}
\author[ncatsu]{R.~Pedroni}
\author[jlab]{L.~Pentchev}
\author[gsi]{K.J.~Peters}
\author[gwu]{W.~Phelps}
\author[jlab]{J.~Pierce\fnref{f10}}
\fntext[f10]{Current address: Oak Ridge National Laboratory, Oak Ridge, TN 37831.}
\author[uofr]{E.L.~Plummer\fnref{f11}}
\fntext[f11]{Current address: Plummer.}
\author[jlab]{E.~Pooser}
\author[uconn]{B.~Pratt}
\author[jlab]{Y.~Qiang\fnref{f12}}
\fntext[f12]{Current address: Toshiba Medical Research Institute USA, Inc., 706 N Deerpath Dr, Vernon Hills, IL 60061.}
\author[nw]{N.~Qin}
\author[jlab]{V.~Razmyslovich\fnref{f13}}
\fntext[f13]{Current address: Razmyslovich.}
\author[fsu]{J.~Reinhold}
\author[asu]{B.G.~Ritchie}
\author[juelich]{J.~Ritman}
\author[nw]{L.~Robison}
\author[mephi]{D.~Romanov}
\author[usm]{C.~Romero}
\author[nsu]{C.~Salgado}
\author[jlab]{N.~Sandoval}
\author[wm]{A.M.~Schertz}
\author[juelich]{S.~Schadmand}
\author[cmu]{R.A.~Schumacher}
\author[gsi]{C.~Schwarz}
\author[gsi]{J.~Schwiening}
\author[uofr]{A.Yu.~Semenov}
\author[uofr]{I.A.~Semenova}
\author[nw]{K.K.~Seth}
\author[ihep]{X.~Shen}
\author[iu]{M.R.~Shepherd}
\author[jlab]{E.S.~Smith\corref{cor}}
\cortext[cor]{Corresponding author: Tel.: +1 757 269 7625.}  
\ead{elton@jlab.org}
\author[cua]{D.I.~Sober}
\author[jlab]{A.~Somov}
\author[mephi]{S.~Somov}
\author[usm]{O.~Soto}
\author[asu]{N.~Sparks}
\author[cmu]{M.J.~Staib}
\author[jlab]{C.~Stanislav}
\author[wm]{J.R.~Stevens}
\author[gwu]{I.I.~Strakovsky}
\author[iu]{A.~Subedi}
\author[uofr]{K.~Suresh}
\author[itep]{V.V.~Tarasov}
\author[jlab]{S.~Taylor}
\author[uofr]{L.A.~Teigrob\fnref{f15}}
\fntext[f15]{Current address: Teigrob.}
\author[uofr]{A.~Teymurazyan}
\author[glasgow]{A.~Thiel}
\author[mephi]{I.~Tolstukhin\fnref{f16}}
\fntext[f16]{Current address: Argonne National Lab.}
\author[nw]{A.~Tomaradze}
\author[usm]{A.~Toro}
\author[fsu]{A.~Tsaris}
\author[cmu]{Y.~Van~Haarlem\fnref{f17}}
\fntext[f17]{Current address: Commonwealth Scientific and Industrial Research Organisation, Lucas Heights, NSW~2234, Australia.}
\author[uofa]{G.~Vasileiadis}
\author[usm]{I.~Vega}
\author[iu]{G.~Visser}
\author[uofa]{G.~Voulgaris}
\author[cua]{N.K.~Walford\fnref{f18}}
\fntext[f18]{Current address: AbbVie Deutschland GmbH, Knollstrasse 67061, Ludwigshafen, Germany.}
\author[glasgow]{D.~ Werthm\"uller\fnref{f19}}
\fntext[f19]{Current address: University of York, York YO10 5DD, United Kingdom.}
\author[jlab]{T.~Whitlatch}
\author[odu]{N.~Wickramaarachchi}
\author[mit]{M.~Williams}
\author[jlab]{E.~Wolin\fnref{f20}}
\fntext[f20]{Current address: 2808 Linden Ln, Williamsburg, VA 23185.}
\author[nw]{T.~Xiao}
\author[mit]{Y.~Yang}
\author[uofr]{J.~Zarling}
\author[wuhan]{Z.~Zhang}
\author[ihep]{Q.~Zhou}
\author[wuhan]{X.~Zhou}
\author[jlab]{B.~Zihlmann}
\address[asu]{Arizona State University, Tempe, Arizona 85287, USA}
\address[uofa]{National and Kapodistrian University of Athens, 15771 Athens, Greece}
\address[cmu]{Carnegie Mellon University, Pittsburgh, Pennsylvania 15213, USA}
\address[cua]{Catholic University of America, Washington, D.C. 20064, USA}
\address[uconn]{University of Connecticut, Storrs, Connecticut 06269, USA}
\address[fiu]{Florida International University, Miami, Florida 33199, USA}
\address[fsu]{Florida State University, Tallahassee, Florida 32306, USA}
\address[gwu]{The George Washington University, Washington, D.C. 20052, USA}
\address[glasgow]{University of Glasgow, Glasgow G12 8QQ, United Kingdom}
\address[gsi]{GSI Helmholtzzentrum f\"ur Schwerionenforschung GmbH, D-64291 Darmstadt, Germany}
\address[iu]{Indiana University, Bloomington, Indiana 47405, USA}
\address[ihep]{Institute of High Energy Physics, Beijing 100049, People's Republic of China}
\address[itep]{Alikhanov Institute for Theoretical and Experimental Physics NRC (Kurchatov Institute), Moscow, 117218, Russia}
\address[jlab]{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606, USA}
\address[juelich]{Forschungszentrum Juelich}
\address[umass]{University of Massachusetts, Amherst, Massachusetts 01003, USA}
\address[mit]{Massachusetts Institute of Technology, Cambridge, Massachusetts 02139, USA}
\address[mephi]{National Research Nuclear University Moscow Engineering Physics Institute, Moscow 115409, Russia}
\address[nsu]{Norfolk State University, Norfolk, Virginia 23504, USA}
\address[ncatsu]{North Carolina A\&T State University, Greensboro, North Carolina 27411, USA}
\address[uncw]{University of North Carolina at Wilmington, Wilmington, North Carolina 28403, USA}
\address[nw]{Northwestern University, Evanston, Illinois 60208, USA}
\address[odu]{Old Dominion University, Norfolk, Virginia 23529, USA}
\address[uofr]{University of Regina, Regina, Saskatchewan, Canada S4S 0A2}
\address[usm]{Universidad T\'ecnica Federico Santa Mar\'ia, Casilla 110-V Valpara\'iso, Chile}
\address[tomsk]{Tomsk State University, 634050 Tomsk, Russia}
\address[tomskb]{Tomsk Polytechnic University, 634050 Tomsk, Russia}
\address[yerevan]{A. I. Alikhanian National Science Laboratory (Yerevan Physics Institute), 0036 Yerevan, Armenia}
\address[wm]{College of William and Mary, Williamsburg, Virginia 23185, USA}
\address[wuhan]{Wuhan University, Wuhan, Hubei 430072, People's Republic of China}
%  
% \collaboration{The \sc{GlueX} Collaboration}
%
